---
title: "README"
output:
  github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# DSCI521_website-test

Hello to prep for tomorrow lecture where we will be creating a quarto website together:
Pre-Activity Instructions: Creating a Repository on GitHub
1. Create a GitHub Repository
    * Go to GitHub and sign in to your account.
    * Click on New Repository to create a new repository for this project.
    * Name your repository appropriately for the activity, name it "DSCI521_website-test1"
2. Repository Setup Requirements
    * Make sure to:
        * Include a README file: Check the box to add a README to the repository. This will allow you to explain the purpose of the repository and provide essential information about your project.
        * Do not add a .gitignore file: Leave the option for a .gitignore file unchecked.
        * License the repository under Creative Commons 0 (CC0): This will ensure that your project can be freely shared and reused.
3. Final Checks
    * Once you have created the repository, confirm that your repository includes the following:
        * A README file.
        * No .gitignore file.
        * A Creative Commons 0 (CC0) license. 


## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
